Barneby Lives!

### 2023-06-16 scripts/Barneby_Lives.Rmd
site name writing fn

```{r}
sites <- data.frame(
  longitude_dd = runif(15, min = -120, max = -100), 
  latitude_dd = runif(15, min = 35, max = 48)
  ) %>% 
  st_as_sf(coords = c('longitude_dd', 'latitude_dd'))

places <- st_read('../geodata/places/places.shp')

head(places)
```

```{r}

#' gather distance and azimuth from shop to center of town
#'
#' Help provide some simple context between the building and the 
#' @param x an sf/tibble/dataframe of locations with associated nearest locality data
#' @param places_data an sf/dataframe/dataframe which contains coordinates for the locations in the data
distAZE <- function(x, places_data){

  locality <- sf::st_drop_geometry(x)
  locality <- locality[1, 'Locality']

  focal <- places_data[grep(locality, places_data$ID), ]
  if(nrow(focal) > 1){
    union_loc <- sf::st_union(x) |> sf::st_point_on_surface()
    focal <- focal[sf::st_nearest_feature(union_loc, focal),]
  }

  location_from <- sf::st_centroid(focal)

  location_from <- sf::st_transform(location_from, 5070)
  x_planar <- sf::st_transform(x, 5070)
  distances <- sf::st_distance(location_from, x_planar, which = 'Euclidean')

  azy <- nngeo::st_azimuth(
    location_from, 
    x_planar
  )

  distances <- data.frame(
    st_drop_geometry(x),
    Distance = round(as.numeric(distances / 1609.34), 1),
    Azimuth = round(as.numeric(azy), 0),
    geometry = x[,'geometry']
  )

}

>>>>

```{r}
sites <- data.frame(
  longitude_dd = runif(15, min = -120, max = -100), 
  latitude_dd = runif(15, min = 35, max = 48)
  ) %>% 
  st_as_sf(coords = c('longitude_dd', 'latitude_dd'), crs = 4326)

test <- site_writer(sites)
